Response to the defense feedback

### 2021-06-01 Chapter-1/Chapter-1.tex
Updates from Overleaf

However, eliminating side-channel vulnerabilities from real-world software code base is not easy. First, side-channels are a low-level problem in computer systems. As a non-functional property, it can be difficult for programmers to reason about or test.  While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, it either suffers from expensive computation costs or high false positives and false negatives.  Second, most vulnerabilities pose a negligible risk. Although some vulnerabilities result in the key being entirely compromised~\cite{184415, aumuller2002fault}, many others are less severe in reality. Therefore, we need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.  Third, many side-channel vulnerable implementations (e.g., the CRT optimization and lookup tables) have better performance. This is a dilemma between the performance and the security.

@@

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We present the related work of the dissertation in Chapter~\ref{chapter2}. Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables. Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack. Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in a multiple-trace attack. Chapter~\ref{chapter6} concludes the dissertation and proposes the future work.

>>>>

However, eliminating side-channel vulnerabilities from real-world software code base is not easy. First, side-channels are a low-level problem in computer systems. As a non-functional property, it can be difficult for programmers to reason about or test.  While recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities, it either suffers from expensive computation costs or high false positives and false negatives.  Second, most vulnerabilities pose a negligible risk. Although some vulnerabilities result in the key being entirely compromised~\cite{184415, aumuller2002fault}, many others are less severe in reality. Therefore, developers are often reluctant to fixing all of them. We need a proper quantification metric to assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.  Third, many side-channel vulnerable implementations (e.g., the CRT optimization and lookup tables) have better performance. This is a dilemma between the performance and the security.

@@

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We present the related work of the dissertation in Chapter~\ref{chapter2}. Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables. Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack. Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in a multiple-trace attack.
Chapter~\ref{chapter6} and Chapter~\ref{chapter7} discuss limitations of the dissertation and propose the future work.

### 2021-06-01 Chapter-7/Chapter-7.tex
Updates from Overleaf

\chapter{Conclusion}\label{chapter6}
This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification. In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance and precision. In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.

>>>>

\chapter{Conclusion}\label{chapter7}
This dissertation research studies the address-based side-channel leakages in two aspects: detection and quantification. In the side-channel vulnerability detection research, we explore and solve the two bottlenecks in today's automated side-channel vulnerability detection tool, performance and precision. In the side-channel vulnerability quantification research, we propose two different side-channel leakage quantification tools based on information theory.
